A Comparison of Graph Processing Systems

### 2020-09-26 documentation/paper/main.tex
bla
introductin and abstract improvements

\begin{abstract}
Graphs are growing fast and are becoming increasingly popular in many different domains, like \todo{...}
There are several different frameworks that help writing graph algorithms.
They often use different approaches and have significant performance differences on different graphs.
\todo{Giraph nicht NUMA aware, da unten raus nehmen..}
In this paper we compare some state-of-the-art non-uniform memory access (NUMA) aware systems in terms of performance, both on real world and synthetic graphs.
\todo{umformulieren}
Therefore, we consider the three algorithms: Single-Source Shortest-Paths (SSSP), Breadth-First Search (BFS) and PageRank (PR).
We compare not only the time the frameworks indicate, they need to compute, but also the time they actually run and consume resources, and the resulting overhead time.
\end{abstract}

@@

\Affirmation

>>>>

\begin{abstract}
Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.
There are several different frameworks that help writing graph algorithms.
They often use different approaches and have significant performance differences on different graphs.
In this paper we compare some state-of-the-art non-uniform memory access (NUMA) aware systems and Giraph in terms of performance, both on real world and synthetic graphs.
Therefore, we evaluate the three algorithms Single-Source Shortest-Paths (SSSP), Breadth-First Search (BFS) and PageRank (PR).
We compare not only the time the frameworks indicate, they need to compute, but also the time they actually run and consume resources, as well as the resulting overhead time.
\end{abstract}

@@

\clearpage
\pagestyle{empty}
\Affirmation

### 2020-09-26 documentation/paper/sections/introduction.tex
introductin and abstract improvements

Some frameworks were developed to facilitate the writing of parallel and distributed graph algorithms.
One of the most commonly known graph-processing systems is the closed-source, distributed system Pregel \cite{pregel}.
Pregel, as well as some open source versions of it, like Giraph \cite{Giraph} and GraphX \cite{graphx}, was built to handle large graphs reliably and be fault-tolerant on large MapReduce infrastructures.
Due to the lack of cache locality, as these systems are written object-oriented, they provide rather suboptimal performance.
Because of this, many non-uniform memory access (NUMA) aware systems such as Ligra \cite{Ligra}, Polymer \cite{Polymer}, Galois \cite{Galois} and Gemini \cite{Gemini} were introduced.
These systems have some similarities, but many differences \todo{Zu wem}. This results in considerable performance differences on many occasions.
Each systems performance was evaluated at release time with some older graph processing frameworks.
However most of the systems are several years old and some of them have evolved, or are still evolving, these comparisons were often incomplete or are simply outdated today.
Other systems are no longer in use, which also reduces the significance of some of the existing comparisons.

Therefore we compared several state-of-the-art non-uniform memory access (NUMA) aware systems in terms of their performance on three graph algorithms (PageRank, SSSP, BFS).\todo{Frameworks nennen}
The comparison is performed on both real world data sets and synthetic graphs.
To provide a comparison to a non-NUMA aware system, Giraph is included in the testing.
Giraph itself has often been compared to other state-of-the-art systems like Pregel or GraphX.
We also included a comparison of Galois with and without hugepages \cite{hugepages}, and several runs with different numbers of threads to see how it scales.
Where possible, several versions of the algorithms were used, like the push and pull variants.

>>>>

Some frameworks were developed to facilitate the writing of parallel and distributed graph algorithms.
One of the most commonly known graph-processing systems is the closed-source, distributed system Pregel \cite{pregel}.
Pregel, as well as some open source versions of it, like Giraph \cite{Giraph} and GraphX \cite{graphx}, was built to handle large graphs reliably and be fault-tolerant on large MapReduce infrastructures.
Due to the lack of cache locality, as these systems are written object-oriented, they provide rather suboptimal performance.
Because of this, many non-uniform memory access (NUMA) aware systems such as Ligra \cite{Ligra}, Polymer \cite{Polymer}, Galois \cite{Galois} and Gemini \cite{Gemini} were introduced.
The different NUMA aware systems have some similarities, but many differences and differ in the technologies they use.
This results in considerable performance differences on many occasions.
Each systems performance was evaluated at release time with some older graph processing frameworks.
However most of the systems are several years old and some of them have evolved, or are still evolving, these comparisons were often incomplete or are simply outdated today.
Other systems are no longer in use, which also reduces the significance of some of the existing comparisons.

Therefore we compared the state-of-the-art NUMA aware systems Ligra, Polymer, Galois and Gemini in terms of their performance on three graph algorithms PageRank, SSSP, BFS.
The comparison is performed on both real world data sets and synthetic graphs.
To provide a comparison to a non-NUMA aware system, Giraph is included in the testing.
It is like the NUMA aware systems open-source and is still being maintained.
Giraph itself has often been compared to other state-of-the-art systems like Pregel or GraphX.
We also included a comparison of Galois with and without hugepages \cite{hugepages}, and several runs with different numbers of threads to see how it scales.
Where possible, several versions of the algorithms were used, like the push and pull variants.
